### 2021-03-14 assertions/doc/thesis-bernhardt/chapters/2-offline_design.tex
Negation

\section{Transformation}\label{sec:transformation}

\section{Existential quantifier and proofs of correctness}
lksddlkdsfk
- forall/exists -> benefit the most. are there use cases for others? or they implement just "normal" assertion
	-> auf forall sowie exist case genauer eingehen. (counterexample vs. proof; take text from CBF/DNF examples)
- formal set of formulae

>>>>

\section{Transformation}\label{sec:transformation}
Since the validators will check the input parameter for the negation of the formula, it has to be transformed before the compilation. Furthermore, the formula should explicitly state the domain for each quantifier, which will have to be translated into a set of bounds that belong to the random generator representing the respective quantifier. These restrictions are important to avoid wasting resources  through testing values out of the relevant (or legal) scope.
Using the example from the exposé \cite{thiemann_2020},

\subsection{Negation}
The formula is negated using the negation rules of second-order logic and applying De Morgan's laws until the negation is applied to the literals. Universal quantifiers become existential ones and vice versa. The conditions, however, are not affected by the negation, since the domain stays the same. This is also reflected in the rules of predicate logic - if the bounds are given as a premise in the logical formula, its negation is equivalent.

\subsection{Defining the domain of random generators}
In some cases, however, implicit boundaries are given by the data type itself. List indices, for instance, are always bound to the range $0.. size(list) - 1$ and could thus be derived from the formula without an explicit specification. As this deduction makes the transformation more complex, as it requires a semantic analysis of the formula, a completely explicit formula in terms of the domain is required for now. Depending on the virtual machine, the lower bound for indexing operations can be handled by the random generator of an appropriate predicate type. As an example, Michelson supports the data type \texttt{nat} representing the natural numbers, which categorically excludes all values below zero.

\section{Existential quantifier and proofs of correctness}
Bisher, alle examples used univeral quantification and checks for counterexamples.
- forall/exists -> benefit the most. are there use cases for others? or they implement just "normal" assertion
	-> auf forall sowie exist case genauer eingehen. (counterexample vs. proof; take text from CBF/DNF examples)
- formal set of formulae
